\documentclass[a4paper, landscape, 10pt]{scrartcl} 
\usepackage[utf8]{inputenc} 
\usepackage[danish]{babel} 
\usepackage[T1]{fontenc}
\usepackage{multicol}
\usepackage[landscape]{geometry}
\usepackage{textcomp}
\usepackage{palatino}
\usepackage{amssymb}
\usepackage[os=win]{menukeys}
\renewmenumacro{\keys}[+]{shadowedroundedkeys}
\usepackage{hyperref}
\hypersetup{
  hidelinks
}

\begin{document}
\thispagestyle{empty}

\section*{iOS VoiceOver Cheatsheet (version-$\alpha$) - ole@omgwtf.dk}

\hrulefill{}

\begin{multicols}{2}

\subsection*{Starting and stopping VoiceOver}
\begin{itemize}
\item{Start VoiceOver with \emph{Siri}: "Turn VoiceOver on".}
\item{Stop VoiceOver with \emph{Siri}: "Turn VoiceOver off".}
\end{itemize}

\subsection*{Setting up VoiceOver}
Open your \textbf{\textit{Settings}} App.
\begin{itemize}
\item{VoiceOver settings: \menu[,]{General,Accessibility,VoiceOver }.}
\end{itemize}

\subsection*{Reading commands}
\begin{itemize}
\item{Use the gesture $\upuparrows$ to read from the top.}
\item{Use the gesture $\downdownarrows$ to read from current position.}
\item{ Use the gesture ($\cdot\cdot$) pauses and restarts reading.}
\end{itemize}

\subsection*{Basic navigation}
\begin{itemize}
\item{Use the gesture $\rightarrow$ to move to next item.}
\item{Use the gesture $\leftarrow$ to move to previous item.}
\item{Use the gesture ($\cdot\cdot$) to activate current item.}
\item{Drag ($\cdot\cdot\cdot$) to scroll.}
\item{Tap ($\cdot\cdot\cdot\cdot$) on top of screen to move to first item.}
\item{Tap ($\cdot\cdot\cdot\cdot$) on bottom of screen to move to last item.}
\item{Zigzag ($\cdot\cdot$) to go back.}
\end{itemize}

\subsection*{Other commands}
\begin{itemize}
\item{ Use the gesture ($\cdot\cdot\cdot$) for information about your localtion.}
\item{ Use the gesture ($\cdot\cdot\cdot$) ($\cdot\cdot\cdot$) to turn speech on and off.}
\item{ Use the gesture ($\cdot\cdot\cdot$)($\cdot\cdot\cdot$)($\cdot\cdot\cdot$) to turn screen on and off.}
\end{itemize}

\subsection*{Magic tap}
The gesture  ($\cdot\cdot$) ($\cdot\cdot$) is known as \textbf{\textit{the magic tap}} and is context dependent.
\begin{itemize}
\item{ Use the gesture ($\cdot\cdot$)($\cdot\cdot$)  to start and stop dictation.}
\item{ Use the gesture ($\cdot\cdot$)($\cdot\cdot$) to pickup you iphone.}
\item{ Use the gesture ($\cdot\cdot$)($\cdot\cdot$) to start and stop playing media.}
\end{itemize}

\subsection*{Using the Rotor}
The rotor is a context-dependent tool. 
\begin{itemize}
\item{Use the rotor-gesture (two-fingers) $\circlearrowleft{}$ or $\circlearrowright$ to set the rotor.}
\item{Use the gesture $\downarrow$ to move to next rotor-item.}
\item{Use the gesture $\uparrow$ to move to previous rotor-item.}
\end{itemize}

\end{multicols}

\hrulefill{}

\end{document}
